### 2022-05-17 paper/introduction.tex
1.add parameter cout to resng/args.json 2. update paper 3. ignore update of args.json

>>>>

%% CNN based methods
The deep convolutional neural network is typically used for image classification, which achieved great success in last several years. \cite{yolov3}, \cite{efficientDet}. 
%% talk about the reason we need new type of network architecture
These kinds of network architecture takes a single image as input which usually employed for classification problems. The image is usually convoluted with convolutional layer and downsampling with pooling layers. The outputs of the network consists of a single value to represent the ID of corresponding class \cite{efficientDet}, or with set of values to represent the position of bounding boxes.\cite{yolov3}.

However, in many other vision tasks, the output is demanded as an image, instead of predicting one or several classes of the input, but the classes of each pixel are predicted. In this case, the traditional network architecture is not suitable anymore.

### 2022-05-17 paper/related_work.tex
1.add parameter cout to resng/args.json 2. update paper 3. ignore update of args.json

@@

%% normal estimation method introduction
Ideally, the normal of each pixel in the depth map can be calculated based on its neighbor pixels constructing a over-determined function systems and solving by algebra methods\cite{geometry_based_solution}. This approach gives a quick but coarse normal inference. It also can be predict directly by feeding the image directly into a CNN \cite{Eigen}, in this case, no depth map is required.
GeoNet\cite{GeoNet} integrates both ideas to refine the coarse normal map with another CNN predicted normal map. 
%% traditional methods

In 2012, Holzer et al. \cite{Holzer.S} presented a read-time method, which is able to run algorithm in a high frame speed. They smooth the depth data in order to handle the noise of depth image. The speed is accelerated via integral image. The drawbacks are, as mentioned in the paper, the normals error go up when point depths change severely.

In 2018, Yu et al. \cite{gconv} presented a CNN based method with gated convolutional layer.

In 2018, Hua et al. \cite{guided} presented an approach integrating color image and certainty map into the network to enhance the performance of depth map density.

In 2019, Ben-Shabat et al. \cite{Ben-Shabat_2019_CVPR} presented a CNN based method.

In 2021, Zhou et al.  \cite{zhou2021fast}

%% CNN based methods
The deep convolutional neural network is typically used for image classification, which achieved great success in last several years. \cite{yolov3}, \cite{efficientDet}.

%% talk about the reason we need new type of network architecture
These kinds of network architecture takes a single image as input which usually employed for classification problems. The image is usually convoluted with convolutional layer and downsampling with pooling layers. The outputs of the network consists of a single value to represent the ID of corresponding class \cite{efficientDet}, or with set of values to represent the position of bounding boxes.\cite{yolov3}.

However, in many other vision tasks, the output is demanded as an image, instead of predicting one or several classes of the input, but the classes of each pixel are predicted. In this case, the traditional network architecture is not suitable anymore.

%% talk about image upsampling, unet
Recently, Ronneberger et al proposed an architecture called UNet \cite{unet} for biomedical image segmentations. The architecture is shown in Figure \ref{fig:u-net}.The first half network is a usual classification convolutional network, the second half replace the pooling layers to upsampling layers, thus in the end of the second half, the output is back to the input size. The proposed network can successfully assigned each pixel a class for segmentation tasks. Under this symmetric network, an input image is downsampled 3 times and upsampled 3 times. Output image has exactly the same size as input image. The downsampling and upsampling both have large number of feature channels, which guarantee the network propagates the information to higher resolution layers.

@@

%% guided scene completion

>>>>

Guided method \cite{guided} requires addition information like RGB image or the certainty map of depth map, and fuse them together to predict the dense depth map.

@@

%% normal estimation method introduction
Usually, we based on point cloud, depth map or RGB/Grayscale image of the objects or scenes to inference the normals.

Traditional methods evaluate normals based on neighbor information of point cloud or depth map.
In 2012, Holzer et al. \cite{Holzer.S} proposed method to calculate normal from covariance matrices. 
This method use integral image as input, which is able to run algorithm in a high frame speed. They smooth the depth data in order to handle the noise of depth image. The drawbacks are, as mentioned in the paper, the normals error go up when point depths change severely. In 2013, Fouhey et al. \cite{geometry_based_solution} proposed a method constructing a over-determined function systems to predict normals and solving it 
by algebra methods. Similarly, this approach gives a quick but coarse normal inference.

%% CNN based methods
Recently, CNN based methods improve the performance of image processing to a brand new stage. In 2014, Eigen et al.\cite{Eigen} proposed a method predicting depth map directly from RGB image using CNN. In this case, no depth map is required. In 2016, Laina et al. \cite{img2depth} proposed a deeper network based on ResNet \cite{resnet} with a well designed upsamling part. 
%% guided scene completion
In 2018, Qi et al. proposed GeoNet\cite{GeoNet}, it integrates both algebra method and also CNN method to inference depthmap based on \cite{img2depth} \cite{geometry_based_solution}.

%% upsampling 
It is worth to noticed that, the output of normal inference CNN model is not one or severl labels but an entire image or normal map with same size. 
%% talk about image upsampling, unet
Recently, Ronneberger et al proposed an architecture called UNet \cite{unet} for biomedical image segmentations. The architecture is shown in Figure \ref{fig:u-net}.The first half network is a usual classification convolutional network, the second half replace the pooling layers and traditional fc layers in the traditional CNNs to upsampling layers, thus in the end of the second half, the output is able to back to the input size. The proposed network can successfully assigned each pixel a class for segmentation tasks. Under this symmetric network, an input image is downsampled 3 times and upsampled 3 times. Output image has exactly the same size as input image. The downsampling and upsampling both have large number of feature channels, which guarantee the network propagates the information to higher resolution layers.

@@

%% unstructured point cloud 
In some case, the input is unstructured point cloud which can not be fed into a CNN entirely. Thus, a challenge task connect to the deep learning is the input format. Since different point clouds have different sizes. 
In 2018, Ben-Shabat et al. \cite{Ben-Shabat_2019_CVPR} presented Nesti-Net. It predicts the normal point by point with the help of neighbor points. It fixed the distance of considering neighbors to provide an unified input for CNN. In 2021, Zhou et al. \cite{zhou2021fast} presents a method considering overlapping of different patches (a group of neighboring points) as input to evaluate normals.
